Understanding of Schizophrenia

### 2021-01-24 chapter1.Rmd
version 0.02

)

[![Malleus Malleficarum (retrieved from Wikipedia)](images/img_0.png){width="50%"}](https://en.wikipedia.org/wiki/Malleus_Maleficarum#/media/File:J._Sprenger_and_H._Institutoris,_Malleus_maleficarum._Wellcome_L0000980.jpg)

@@

[![A Dementia Praecox patient with Catatonia](images/img_1.png){width="50%"}](https://upload.wikimedia.org/wikipedia/commons/9/9c/Writing_on_the_back_of_a_female_patient_Wellcome_L0040284.jpg)

@@

# References

>>>>

[![Malleus Malleficarum (retrieved from Wikipedia)](images/img_0.png){.center width="50%"}](https://en.wikipedia.org/wiki/Malleus_Maleficarum#/media/File:J._Sprenger_and_H._Institutoris,_Malleus_maleficarum._Wellcome_L0000980.jpg)

@@

[![A Dementia Praecox patient with Catatonia](images/img_1.png){.center width="50%"}](https://upload.wikimedia.org/wikipedia/commons/9/9c/Writing_on_the_back_of_a_female_patient_Wellcome_L0040284.jpg)

@@
